\section{Introduction}
Accessibility to public transit has been long established as a key factor influencing the price of residential properties, particularly in dense urban environments where vehicle mobility is greatly constrained \citep{rietveld_2007}.
 In the context of the Greater London Area subway stations are the most efficient method of transportation for most commuters and thereby play a critical role in shaping the greater housing market.
  To this end in this paper we investigate how the euclidean distance from a residence to its nearest subway station affects market price.

By focusing on the Greater London Area our study contributes to already established relationships between subway proximity and house prices. 
Early studies such as those done by \citet{muth_1969} are cornerstones in establishing a relationship between densification and land use in cities. 
More recently a greater number of studies have found a significant positive relationship between transit proximity and real estate prices 
in cities such as those in Shanghai \citep{zhou_2019} where subway stations proximity was specifically correlated to 
increased house prices at statistically significant results. 
However London presents unique opportunities for research. 
As the historical pioneer in subway technology the city has had 
the opportunity to develop around an already established subway system and culture.

In our analysis we investigate two effects, the premium associated with being marginally closer to a subway station,
as well as the threshold effect of being within a certain distance of a subway station. We find precise null effects for the marginal
distance on house price. \citet{rietveld_2007} finds that 
the price effect of subway stations on commercial buildings is present at short distances, we find the same results for London house prices, setting a 2km threshold.


The rest of the paper is structured as follows: Section \ref{sec:data} describes the data used in this analysis.
Section \ref{sec:regression_analysis} outlines the methodology and model specifications used to measure the subway effect,
 and presents the results of our analysis. Section \ref{sec:conclusion} discusses the limitations of our methodology and concludes.
  Appendix \ref{sec:appendix} holds figures and tables.
