\section{Data}
\label{sec:data}
We begin our analysis by sourcing data from ONS, the national statistics arm of the UK government,
 which provides panel data containing each lease transfers (home sale) that occurred in the U.K. from 1995 to today \citep{land_ukgov}.
  We prune this dataset to only contain observations within the Greater London Area.
   This dataset amounts to approximately 350 thousand observations. Each unit of observation represents
    a single lease transfer in London containing the date, coordinates, neighborhood, and house price in British Pounds during the transfer.
      We also sourced the coordinates of every subway station in the
      London Underground and the date at which it was opened \citep{subway_wikipedia}. 
We combine the subway and housing datasets, finding the closest subway station to each house at the time of the lease transfer using euclidean distances based on latitude and longitude.
Delving into the summary statistics of our data, we can look at how the data is spread
 across our different variables. For our main variable of interest, the distance to subway stations, we see an
  average distance of 2821 meters with a variance of 2915 meters (Table~\ref{tab:continuous_summary_stats}). On average houses are located quite far from
   a subway station but also contain vast amounts of variation. Houses are clustered around subway stations therefore we end up with long tails, a few houses that are very far away bringing kurtosis to our data.
    We truncate these outliers at 10km, and the distribution of the minimum distance to a subway station can be seen in Figure~\ref{min_dist_distribution}.
     Raw house price is also right skewed with a long tail, so we take the log of house prices to make our regression more interpretable
      and the distribution of log price can be seen in Figure~\ref{log_price_distribution}.
We see that our houses are very evenly spread between our neighborhood controls with the largest
 neighborhood only being 2 points off of the mean (Table~\ref{tab:summary_district}). Similarly, our lease transfers are also evenly spread between years
  with each year accounting for approximately 2\% 
  of our dataset (Table~\ref{tab:summary_year}). This is good for the robustness of our future models as every neighbourhood and year is well represented. 
  On the other hand the spread between newly built and old homes is skewed with 97\%
   of lease transfers coming from the sale of pre-owned homes(Table~\ref{tab:summary_ON}). As a result it may be more sensitive to outliers.
