\documentclass[11pt,a4paper,english]{article}
\usepackage{natbib}  % Adds support for different citation styles
\bibliographystyle{chicago}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{babel}
\usepackage{blindtext}
\usepackage[nodayofweek,level]{datetime}
\newdate{date}{05}{12}{2024}
\date{\displaydate{date}}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{longtable}
\doublespacing



\title{Analyzing the effects of Subway proximity on real estate prices in London 
\thanks{Code and data supporting this analysis is available at: \url{https://github.com/Aman-Rana-02/Subway_Proximity_and_House_Prices}}}
\author{%
  Aman Rana \\ 1007034692 \\ aman.rana@mail.utoronto.ca
  \and
  Pierre Sarrailh \\ 1006770111 \\ pierre.sarrailh@mail.utoronto.ca
}
\date{}
\begin{document}
  \maketitle
  \begin{center}
    ECO375: Applied Econometrics \\ 
    University of Toronto \\ 
    Department of Economics \\
    5\textsuperscript{th} December, 2024
  \end{center}

  \begin{abstract}
    \noindent Following \citet{zhou_2019} we saw that the completion of subway lines increased the prices of real estate in their proximity. Our contribution will be to look at these effects in London. 
     We found precise null effects by a multivariate linear regression of distance from a station on the log of house prices, with controls for time and district. In a regression of log price on the distance 
     from the nearest station with time and district controls, the slope coefficient is -0.0000268 with a standard error of 0.000000687, 
     a statistically significant relationship of such small effect it led us to conclude precise null effects. 
     The effect is economically insignificant, even a 10km distance from a station (which is above the 95th 
     percentile of our distance data) would lead to only a 0.2\% decrease in house price. 
     On more relative terms, a standard deviation difference in distance is only associated with a 
     14\% of a standard deviation change in log house price. 
     A possible further investigation would be to look at the treatment effect of having a 
     nearer subway station using a difference-in-difference (DiD) framework. 
     Using the DiD framework we would be aiming to investigate the effect of specifically 
     new subway stations on house prices while accounting standardizing over previously built ones.
  \end{abstract}

  % \newpage
  % \tableofcontents

  \newpage
  \input{00-introduction}

  \input{01-data}

  \input{02-regression_analysis}

  \input{03-conclusion}

  \newpage
  \bibliographystyle{chicago}
  \bibliography{references}

  \newpage
  \section*{Appendix}
  \renewcommand{\thesection}{\Alph{section}}
  \setcounter{section}{0}
  \input{05-appendix}
\end{document}